Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2012-07-23 doc/asplos13/evaluation.tex
add the no aggreagiton uts plot`
added some plots

%% UTS: performance comparison
\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/uts_compare.pdf}
    \end{center}
    \caption{Performance of in-memory unbalanced tree search. Grappa
        keeps scaling through 128 nodes and beats the XMT with 16
        nodes.}
    \label{fig:uts_compare}
\end{figure}

@@

\begin{figure}[tH]
\begin{center}
  \includegraphics[width=0.95\columnwidth]{figs/bfs_compare}
\begin{minipage}{0.95\columnwidth}
  \caption{\label{fig:bfs-performance} BFS performance}
\end{minipage}
\vspace{-3ex}
\end{center}
\end{figure}

@@

\begin{figure}[tH]
\begin{center}
  \includegraphics[width=0.95\columnwidth]{figs/centrality-performance}
\begin{minipage}{0.95\columnwidth}
  \caption{\label{fig:centrality-performance} Centrality performance}
\end{minipage}
\vspace{-3ex}
\end{center}
\end{figure}

@@

@@

\begin{figure}[htb]
\begin{center}
  \includegraphics[width=0.95\columnwidth]{figs/bfs_sweep_workers}
\begin{minipage}{0.95\columnwidth} 
  \caption{\label{fig:bfs-sweep-workers} Sensitivity to maximum active tasks}
\end{minipage}
\vspace{-3ex}
\end{center}
\end{figure}

>>>>

%% UTS: performance comparison
\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/uts_performance.pdf}
    \end{center}
    \caption{Performance of in-memory unbalanced tree search.}
    \label{fig:uts_compare}
\end{figure}

@@

\begin{figure}[tH]
\begin{center}
  \includegraphics[width=0.95\columnwidth]{figs/bfs_performance}
\begin{minipage}{0.95\columnwidth}
  \caption{\label{fig:bfs-performance} BFS performance}
\end{minipage}
\vspace{-3ex}
\end{center}
\end{figure}

@@

\begin{figure}[tH]
\begin{center}
  \includegraphics[width=0.95\columnwidth]{figs/centrality_performance}
\begin{minipage}{0.95\columnwidth}
  \caption{\label{fig:centrality-performance} Centrality performance}
\end{minipage}
\vspace{-3ex}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
  \includegraphics[width=0.95\columnwidth]{figs/no_aggregation_uts.pdf}
\begin{minipage}{0.95\columnwidth}
  \caption{\label{fig:no-aggregation-uts} Performance of UTS on 16
      nodes with and without Grappa's aggregation.}
\end{minipage}
\vspace{-3ex}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
  \includegraphics[width=0.95\columnwidth]{figs/worker_sweep}
\begin{minipage}{0.95\columnwidth} 
  \caption{\label{fig:bfs-sweep-workers} Sensitivity to maximum active tasks}
\end{minipage}
\vspace{-3ex}
\end{center}
\end{figure}
